Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
review axhttp

%%Describe the change 
Version 2.0 of the API was designed to be event-driven system which makes use of callbacks. To achieve this, the old event system had to be re-designed. The new event system is used by all features of version 2.0. An example of when an event is generated is when movement is detected by the camera.

%%Relate it to Categories
Given that this module was a re-implementation previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative. Groomative was chosen as the secondary category due to the additional motive of bringing the new feature in line with the new interface.

%%What she said 
The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system. The interviewee expressed that they were unsatisfied with certain usability aspects of the API. event was then completely re-implemented and as a secondary concern, adopted the new system design being used in version 2.0

%%Category based on her information
From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.

@@

%%Describe the change 
axhttp was re-implemented from the previous version of the API to follow the new interface and callbacks standards while also including the event driven architecture of 2.0. Functionality remained similar in that it allowed the conversion of data into html in order to display on web pages.

>>>>

%%Describe the change 
Version 2.0 of the API was designed to be an event-driven system which makes use of callbacks. To achieve this, the old event system had to be re-designed. The new design is used by all features of API version 2.0. An example of when an event is generated is when movement is detected by the camera.

%%Relate it to Categories
Given that this module was a re-implementation of the previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative. Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.

%%What she said 
The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system. One reason being that the case company were dissatisfied with certain usability aspects of the API. The module was then completely re-implemented and according to the new system design of version 2.0.

%%Category based on her information
From the discussion in the interview, it was clear that both of our categorisations were correct. The change was primarily enhancive and secondarily groomative.

@@

%%Describe the change 
The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynically load data to web pages. The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards. Additional functionality was also added to the module.
